---
title: "case_study"
author: "Fang Liu (fl2569)"
date: "10/114/2021"
output: github_document
---

```{r eval=FALSE}
#tidyverse pacakge (dplyr, ggplot2, etc)
library(tidyverse)
library(dyplyr)

#figure size options
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

#set theme settings
theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

#### Load dataset
```{r load_data}
library(p8105.datasets)
data(nyc_airbnb)
```

* How many rentals are there? of what type? in what places?
* Is price correlated with review score? 
* Which neighborhood is most popular? Most expensive? 
* Is availability related to price? 
* Room type related to neighborhood?
* Average length of stay related to neighborhood group/borough? 

```{r}
nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(stars = review_scores_location / 2) %>% 
  rename(borough = neighbourhood_group)
  #review score is from 1- 10 --> want 1-5
```

```{r}
nyc_airbnb %>% 
  janitor::tabyl(borough, room_type) 
```

# Which neighborhood is most expensive? 

# Price vs. borough 
```{r most_expensive}
example =
  nyc_airbnb %>%
  select(borough, price) %>% 
  drop_na() %>% 
  group_by(borough) %>% 
  summarize(
    mean_price = mean(price)
  ) %>% 
  arrange(mean_price)

example  
```

# price vs. ratings
```{r most_popular}
example2 =
  nyc_airbnb %>% 
  select(borough, price, review_scores_location) %>% 
  drop_na() %>% 
  group_by(borough) %>% 
  summarize(
    mean_price = mean(price),
    mean_review = mean(star)
  ) %>% 
  arrange(mean_review, mean_price)

example2  
```

# price vs. ratings
```{r}
nyc_airbnb %>% 
  ggplot(aes(x= review_scores_location, y=price))+
  geom_point()
```

Which neibhorhood in manhatten is the most expensive?
```{r}
example =
  nyc_airbnb %>%
  filter(borough == "Manhaten") %>% 
  drop_na() %>% 
  group_by(neighbourhood) %>% 
  summarize(
    mean_price = mean(price)
  ) %>% 
  arrange(mean_price)

example
```


`sample_n` gives us a random sample of size x
```{r}
nyc_airbnb %>% 
  filter(price < 400) %>% 
  sample_n(5000) %>% 
  ggplot(aes(x = lat, y = long, color = price)) +
  geom_point()
```

## retry leaflet
```{r}
library(leaflet)

pal = colorNumeric("viridis", NULL)


nyc_airbnb %>% 
  filter(price < 500) %>% 
  sample_n(1000) %>% 
  leaflet() %>% 
  addTiles() %>% 
  addCircleMarkers(
    ~lat, ~long, color = ~pal(price))
```

### Website for references 
[Intro to leaflet](https://teachdatascience.com/leaflet/)
[Leaflet](https://rstudio.github.io/leaflet/) 





